### 2024-02-06 README.Rmd
added subsections
with uk map data in inst/ext folder

uk_map_download <- st_read(
  "https://services1.arcgis.com/ESMARspQHYMw9BZ9/arcgis/rest/services/WPC_Dec_2019_UGCB_UK_2022/FeatureServer/0/query?outFields=*&where=1%3D1&f=geojson",
  quiet = TRUE)

@@

@@

@@

fit <- readRDS("brmsfit_degree.rds")

>>>>

# uk_map_download <- st_read(
#   "https://services1.arcgis.com/ESMARspQHYMw9BZ9/arcgis/rest/services/WPC_Dec_2019_UGCB_UK_2022/FeatureServer/0/query?outFields=*&where=1%3D1&f=geojson",
#   quiet = TRUE)

uk_map_download <- st_read(
  "inst/extdata/WPC_Dec_2019_UGCB_UK.shp",
  quiet = TRUE)

@@

#### Remove islands

@@

#### Connect islands

@@

fit <- readRDS("/Users/kevinhoran/Documents/sfislands_prepstuff/brmsfit_degree.rds")
